### 2022-12-08 SALT-abstract/SALT-abstract.tex
added model summaries, fixed references + formatting issues

\documentclass[12pt, a4paper]{scrartcl}

@@

\noindent 
We present experimental evidence that i) the projection of the content of the clausal complement of attitude predicates varies across entailment-canceling operators (negation, question, modal, conditional) and ii) this by-operator variation differs across attitude predicates. Our results do not align with the long-standing distinction between factive and semi-factive predicates (see, e.g., \citealt{karttunen_observations_1971,djarv_cognitive_2018}). Instead, the observed by-operator variation groups predicates by lexical semantic/pragmatic properties that raise important questions for future research on projection.

@@

	\vspace{-.4\baselineskip}
	% Previous work on projection showed that it is not a categorial property of lexical triggers \citep{tonhauser_how_2018}, but a gradient one, affected by various contextual factors \citep{simons_what_2010,de_marneffe_did_2012,beaver_questions_2017,degen_prior_2021}. In light of this, we expect that the hetergeneous entailment-cancelling operators in \ref{ex:family} affect projection differentially.
	%
	\citealt{karttunen_observations_1971} suggested that the CC of factive predicates (e.g., \emph{regret, forget}) projects from under all four operators, whereas that of semi-factive predicates (e.g., \emph{discover, realize, see, notice}) always projects from under negation, but not always from under polar questions, modals, or conditionals.

@@

\noindent
{\bf Experiment.} We present the results of an experiment designed to investigate by-operator projection variation for the CCs of 20 attitude predicates, including purported factive and semi-factive predicates (e.g., \emph{be annoyed, discover}). Projection was measured for the same contents across all four operators in \ref{ex:family} using the `certain that' diagnostic for projection (see also, e.g., \citealt{tonhauser_how_2018, djaerv-bacovcin-salt27, mahler2020}).

@@

We observe that projection varies by predicate (e.g., the CC of \emph{be annoyed} is more projective than that of \emph{discover}; replicating the results of  \citealt{degen-tonhauser-language}).

@@

>>>>

\documentclass[12pt, a4paper]{article}

@@

\noindent 
We present experimental evidence that i) the projection of the content of the clausal complement of attitude predicates varies across entailment-canceling operators (negation, question, modal, conditional) and ii) this by-operator variation differs across attitude predicates. Our results do not align with the long-standing distinction between factive and semi-factive predicates (see, e.g., \citealp{karttunen_observations_1971,hooper_applicability_1973,djarv_cognitive_2018}, though see \citealp{beaver_have_2010}). Instead, the observed by-operator variation groups predicates by lexical semantic/pragmatic properties that raise important questions for future research on projection.

@@

	\vspace{-.4\baselineskip}
	% Previous work on projection showed that it is not a categorial property of lexical triggers \citep{tonhauser_how_2018}, but a gradient one, affected by various contextual factors \citep{simons_what_2010,de_marneffe_did_2012,beaver_questions_2017,degen_prior_2021}. In light of this, we expect that the hetergeneous entailment-cancelling operators in \ref{ex:family} affect projection differentially.
	%
	\citet{karttunen_observations_1971} proposed that the CC of factive predicates (e.g. \emph{regret, forget}) projects from under all four operators, whereas that of semi-factive predicates (e.g. \emph{discover, realize, see, notice}) always projects from under negation, but not always from under polar questions, modals, or conditionals.

@@

	\noindent
	{\bf Experiment.} We present the results of an experiment designed to investigate by-operator projection variation for the CCs of 20 attitude predicates, including purported factive and semi-factive predicates (e.g., \emph{be annoyed, discover}). Projection was measured for the same contents across all four operators in \ref{ex:family} using the `certain that' diagnostic for projection (see also, e.g., \citealt{tonhauser_how_2018,djarv_prosodic_2017, mahler2020}).

@@

We observe that projection varies by predicate (e.g., the CC of \emph{be annoyed} is more projective than that of \emph{discover}; replicating the results of \citealp{degen_are_2022}).

@@

\begin{table}[ht]
	\caption{Model output w \texttt{be\_annoyed/n} as baseline}
	\label{tab:annoyed-n}
	\centering

	\begin{tabular}{lrrrrr}
		\toprule
		  & Estimate & Std. Error & df & t value & Pr(>|t|)\\
		\midrule
		(Intercept) & 0.8669958 & 0.0114402 & 1479.204 & 75.7850523 & 0.0000000\\
		opc & -0.1155850 & 0.0156641 & 26227.368 & -7.3789836 & 0.0000000\\
		opm & -0.1564480 & 0.0155858 & 26288.139 & -10.0378702 & 0.0000000\\
		opq & 0.0249138 & 0.0143090 & 56826.915 & 1.7411232 & 0.0816674\\
		verbsuggest & -0.6162683 & 0.0134941 & 54372.895 & -45.6694112 & 0.0000000\\
		\addlinespace
		verbacknowledge & -0.2204417 & 0.0134948 & 54373.777 & -16.3352724 & 0.0000000\\
		verbadmit & -0.3402430 & 0.0134933 & 54371.874 & -25.2156750 & 0.0000000\\
		verbannounce & -0.3607504 & 0.0134931 & 54371.547 & -26.7359958 & 0.0000000\\
		verbbe\_right & -0.6638924 & 0.0134936 & 54372.293 & -49.2003974 & 0.0000000\\
		verbconfess & -0.3681695 & 0.0134949 & 54373.904 & -27.2820517 & 0.0000000\\
		\addlinespace
		verbconfirm & -0.6338363 & 0.0134931 & 54371.657 & -46.9746939 & 0.0000000\\
		verbdemonstrate & -0.5307026 & 0.0134935 & 54372.157 & -39.3301466 & 0.0000000\\
		verbdiscover & -0.1864716 & 0.0134942 & 54372.992 & -13.8186520 & 0.0000000\\
		verbestablish & -0.5542561 & 0.0134933 & 54371.853 & -41.0764079 & 0.0000000\\
		verbhear & -0.1956794 & 0.0134938 & 54372.473 & -14.5014554 & 0.0000000\\
		\addlinespace
		verbinform & -0.1374428 & 0.0134945 & 54373.345 & -10.1851106 & 0.0000000\\
		verbknow & -0.0748953 & 0.0134936 & 54372.288 & -5.5504197 & 0.0000000\\
		verbpretend & -0.5049533 & 0.0134944 & 54373.218 & -37.4195409 & 0.0000000\\
		verbprove & -0.6364950 & 0.0134935 & 54372.138 & -47.1704273 & 0.0000000\\
		verbreveal & -0.3057814 & 0.0134937 & 54372.418 & -22.6609884 & 0.0000000\\
		\addlinespace
		verbsay & -0.5419725 & 0.0134925 & 54370.770 & -40.1685159 & 0.0000000\\
		verbsee & -0.1827512 & 0.0134932 & 54371.791 & -13.5438968 & 0.0000000\\
		verbthink & -0.5101198 & 0.0134930 & 54371.491 & -37.8062103 & 0.0000000\\
		opc:verbsuggest & 0.1594325 & 0.0190634 & 54372.626 & 8.3632939 & 0.0000000\\
		opm:verbsuggest & 0.1766113 & 0.0189718 & 54372.046 & 9.3091498 & 0.0000000\\
		\addlinespace
		opq:verbsuggest & -0.0737648 & 0.0192906 & 54372.717 & -3.8238781 & 0.0001315\\
		opc:verbacknowledge & 0.1945569 & 0.0190630 & 54372.333 & 10.2059764 & 0.0000000\\
		opm:verbacknowledge & 0.1100553 & 0.0189729 & 54373.070 & 5.8006461 & 0.0000000\\
		opq:verbacknowledge & 0.0672935 & 0.0192909 & 54372.991 & 3.4883599 & 0.0004864\\
		opc:verbadmit & 0.2803349 & 0.0190626 & 54371.933 & 14.7060204 & 0.0000000\\
		\addlinespace
		opm:verbadmit & 0.1810708 & 0.0189717 & 54371.994 & 9.5442376 & 0.0000000\\
		opq:verbadmit & 0.0440050 & 0.0192896 & 54371.832 & 2.2812856 & 0.0225354\\
		opc:verbannounce & 0.2503929 & 0.0190639 & 54373.132 & 13.1343759 & 0.0000000\\
		opm:verbannounce & 0.1633026 & 0.0189721 & 54372.338 & 8.6075049 & 0.0000000\\
		opq:verbannounce & 0.0017532 & 0.0192899 & 54372.121 & 0.0908892 & 0.9275810\\
		\addlinespace
		opc:verbbe\_right & 0.1424317 & 0.0190623 & 54371.698 & 7.4718895 & 0.0000000\\
		opm:verbbe\_right & 0.2582399 & 0.0189717 & 54371.967 & 13.6118412 & 0.0000000\\
		opq:verbbe\_right & -0.0776846 & 0.0192897 & 54371.974 & -4.0272512 & 0.0000565\\
		opc:verbconfess & 0.3111230 & 0.0190643 & 54373.455 & 16.3196605 & 0.0000000\\
		opm:verbconfess & 0.1837114 & 0.0189741 & 54374.125 & 9.6821973 & 0.0000000\\
		\addlinespace
		opq:verbconfess & 0.0393640 & 0.0192890 & 54371.320 & 2.0407459 & 0.0412809\\
		opc:verbconfirm & 0.2963833 & 0.0190629 & 54372.237 & 15.5476205 & 0.0000000\\
		opm:verbconfirm & 0.3663333 & 0.0189721 & 54372.324 & 19.3090505 & 0.0000000\\
		opq:verbconfirm & 0.0312870 & 0.0192902 & 54372.377 & 1.6219108 & 0.1048282\\
		opc:verbdemonstrate & 0.2854366 & 0.0190647 & 54373.829 & 14.9719656 & 0.0000000\\
		\addlinespace
		opm:verbdemonstrate & 0.2783816 & 0.0189716 & 54371.830 & 14.6736292 & 0.0000000\\
		opq:verbdemonstrate & 0.0753554 & 0.0192892 & 54371.520 & 3.9066023 & 0.0000937\\
		opc:verbdiscover & 0.2270099 & 0.0190632 & 54372.450 & 11.9082962 & 0.0000000\\
		opm:verbdiscover & 0.1002424 & 0.0189726 & 54372.795 & 5.2835252 & 0.0000001\\
		opq:verbdiscover & 0.0762282 & 0.0192898 & 54372.014 & 3.9517423 & 0.0000777\\
		\addlinespace
		opc:verbestablish & 0.2570817 & 0.0190633 & 54372.539 & 13.4857080 & 0.0000000\\
		opm:verbestablish & 0.2879581 & 0.0189714 & 54371.677 & 15.1785426 & 0.0000000\\
		opq:verbestablish & 0.0061604 & 0.0192893 & 54371.583 & 0.3193687 & 0.7494481\\
		opc:verbhear & 0.2016309 & 0.0190630 & 54372.273 & 10.5770983 & 0.0000000\\
		opm:verbhear & -0.0046313 & 0.0189714 & 54371.681 & -0.2441216 & 0.8071376\\
		\addlinespace
		opq:verbhear & 0.0756021 & 0.0192902 & 54372.373 & 3.9192008 & 0.0000890\\
		opc:verbinform & 0.1278740 & 0.0190645 & 54373.631 & 6.7074362 & 0.0000000\\
		opm:verbinform & 0.0141486 & 0.0189741 & 54374.122 & 0.7456761 & 0.4558664\\
		opq:verbinform & 0.0587564 & 0.0192913 & 54373.322 & 3.0457537 & 0.0023221\\
		opc:verbknow & 0.1142699 & 0.0190629 & 54372.206 & 5.9943629 & 0.0000000\\
		\addlinespace
		opm:verbknow & 0.0130032 & 0.0189709 & 54371.181 & 0.6854301 & 0.4930755\\
		opq:verbknow & 0.0569598 & 0.0192897 & 54371.975 & 2.9528579 & 0.0031498\\
		opc:verbpretend & -0.0902047 & 0.0190640 & 54373.155 & -4.7316842 & 0.0000022\\
		opm:verbpretend & -0.0194245 & 0.0189738 & 54373.822 & -1.0237558 & 0.3059552\\
		opq:verbpretend & -0.2196823 & 0.0192900 & 54372.250 & -11.3883795 & 0.0000000\\
		\addlinespace
		opc:verbprove & 0.2579585 & 0.0190627 & 54372.031 & 13.5320999 & 0.0000000\\
		opm:verbprove & 0.3580525 & 0.0189720 & 54372.223 & 18.8726898 & 0.0000000\\
		opq:verbprove & 0.0230805 & 0.0192908 & 54372.899 & 1.1964509 & 0.2315259\\
		opc:verbreveal & 0.2902650 & 0.0190644 & 54373.511 & 15.2255216 & 0.0000000\\
		opm:verbreveal & 0.1767476 & 0.0189723 & 54372.513 & 9.3160804 & 0.0000000\\
		\addlinespace
		opq:verbreveal & 0.0665887 & 0.0192906 & 54372.717 & 3.4518763 & 0.0005571\\
		opc:verbsay & 0.1985351 & 0.0190618 & 54371.193 & 10.4153412 & 0.0000000\\
		opm:verbsay & 0.1451974 & 0.0189723 & 54372.495 & 7.6531273 & 0.0000000\\
		opq:verbsay & -0.1815738 & 0.0192889 & 54371.195 & -9.4133926 & 0.0000000\\
		opc:verbsee & 0.2175191 & 0.0190629 & 54372.234 & 11.4105822 & 0.0000000\\
		\addlinespace
		opm:verbsee & 0.0594092 & 0.0189723 & 54372.499 & 3.1313655 & 0.0017409\\
		opq:verbsee & 0.1108274 & 0.0192896 & 54371.840 & 5.7454526 & 0.0000000\\
		opc:verbthink & 0.0023197 & 0.0190619 & 54371.272 & 0.1216913 & 0.9031440\\
		opm:verbthink & 0.0145577 & 0.0189717 & 54371.965 & 0.7673367 & 0.4428847\\
		opq:verbthink & -0.1738342 & 0.0192903 & 54372.438 & -9.0115053 & 0.0000000\\
		\bottomrule
	\end{tabular}
\end{table}

\begin{table}[ht]
	\caption{Model output w \texttt{discover/n} as baseline}
	\label{tab:discover-n}
	\centering

	\begin{tabular}{lrrrrr}
		\toprule
		  & Estimate & Std. Error & df & t value & Pr(>|t|)\\
		\midrule
		(Intercept) & 0.6805242 & 0.0114403 & 1479.217 & 59.4849565 & 0.0000000\\
		opc & 0.1114249 & 0.0156639 & 26226.686 & 7.1134644 & 0.0000000\\
		opm & -0.0562056 & 0.0155855 & 26286.826 & -3.6062779 & 0.0003112\\
		opq & 0.1011420 & 0.0143103 & 56828.295 & 7.0677830 & 0.0000000\\
		verbbe\_annoyed & 0.1864716 & 0.0134942 & 54372.998 & 13.8186521 & 0.0000000\\
		\addlinespace
		verbsuggest & -0.4297967 & 0.0134937 & 54372.361 & -31.8516905 & 0.0000000\\
		verbacknowledge & -0.0339702 & 0.0134936 & 54372.308 & -2.5174950 & 0.0118221\\
		verbadmit & -0.1537714 & 0.0134942 & 54372.985 & -11.3953857 & 0.0000000\\
		verbannounce & -0.1742788 & 0.0134947 & 54373.649 & -12.9145926 & 0.0000000\\
		verbbe\_right & -0.4774208 & 0.0134935 & 54372.079 & -35.3816304 & 0.0000000\\
		\addlinespace
		verbconfess & -0.1816980 & 0.0134936 & 54372.192 & -13.4655376 & 0.0000000\\
		verbconfirm & -0.4473648 & 0.0134944 & 54373.311 & -33.1517710 & 0.0000000\\
		verbdemonstrate & -0.3442310 & 0.0134928 & 54371.247 & -25.5121517 & 0.0000000\\
		verbestablish & -0.3677846 & 0.0134928 & 54371.167 & -27.2579106 & 0.0000000\\
		verbhear & -0.0092079 & 0.0134940 & 54372.798 & -0.6823676 & 0.4950095\\
		\addlinespace
		verbinform & 0.0490288 & 0.0134942 & 54373.066 & 3.6333114 & 0.0002801\\
		verbknow & 0.1115762 & 0.0134931 & 54371.668 & 8.2691029 & 0.0000000\\
		verbpretend & -0.3184818 & 0.0134943 & 54373.176 & -23.6011440 & 0.0000000\\
		verbprove & -0.4500234 & 0.0134934 & 54372.042 & -33.3512833 & 0.0000000\\
		verbreveal & -0.1193099 & 0.0134941 & 54372.880 & -8.8416323 & 0.0000000\\
		\addlinespace
		verbsay & -0.3555009 & 0.0134943 & 54373.168 & -26.3444678 & 0.0000000\\
		verbsee & 0.0037204 & 0.0134930 & 54371.450 & 0.2757288 & 0.7827574\\
		verbthink & -0.3236483 & 0.0134936 & 54372.197 & -23.9853913 & 0.0000000\\
		opc:verbbe\_annoyed & -0.2270099 & 0.0190632 & 54372.453 & -11.9082963 & 0.0000000\\
		opm:verbbe\_annoyed & -0.1002424 & 0.0189726 & 54372.798 & -5.2835253 & 0.0000001\\
		\addlinespace
		opq:verbbe\_annoyed & -0.0762282 & 0.0192898 & 54372.017 & -3.9517423 & 0.0000777\\
		opc:verbsuggest & -0.0675773 & 0.0190625 & 54371.851 & -3.5450396 & 0.0003929\\
		opm:verbsuggest & 0.0763690 & 0.0189709 & 54371.211 & 4.0255864 & 0.0000569\\
		opq:verbsuggest & -0.1499930 & 0.0192910 & 54373.069 & -7.7752981 & 0.0000000\\
		opc:verbacknowledge & -0.0324529 & 0.0190617 & 54371.116 & -1.7025196 & 0.0886637\\
		\addlinespace
		opm:verbacknowledge & 0.0098129 & 0.0189711 & 54371.417 & 0.5172570 & 0.6049789\\
		opq:verbacknowledge & -0.0089347 & 0.0192902 & 54372.396 & -0.4631724 & 0.6432426\\
		opc:verbadmit & 0.0533251 & 0.0190632 & 54372.508 & 2.7972739 & 0.0051554\\
		opm:verbadmit & 0.0808284 & 0.0189728 & 54372.916 & 4.2602367 & 0.0000205\\
		opq:verbadmit & -0.0322232 & 0.0192908 & 54372.883 & -1.6703960 & 0.0948468\\
		\addlinespace
		opc:verbannounce & 0.0233831 & 0.0190642 & 54373.367 & 1.2265427 & 0.2199998\\
		opm:verbannounce & 0.0630602 & 0.0189726 & 54372.754 & 3.3237576 & 0.0008887\\
		opq:verbannounce & -0.0744750 & 0.0192926 & 54374.465 & -3.8602856 & 0.0001134\\
		opc:verbbe\_right & -0.0845782 & 0.0190620 & 54371.360 & -4.4370099 & 0.0000091\\
		opm:verbbe\_right & 0.1579976 & 0.0189719 & 54372.163 & 8.3279685 & 0.0000000\\
		\addlinespace
		opq:verbbe\_right & -0.1539128 & 0.0192901 & 54372.283 & -7.9788617 & 0.0000000\\
		opc:verbconfess & 0.0841131 & 0.0190632 & 54372.437 & 4.4123417 & 0.0000102\\
		opm:verbconfess & 0.0834691 & 0.0189719 & 54372.142 & 4.3996174 & 0.0000109\\
		opq:verbconfess & -0.0368642 & 0.0192905 & 54372.632 & -1.9110088 & 0.0560087\\
		opc:verbconfirm & 0.0693734 & 0.0190644 & 54373.529 & 3.6388992 & 0.0002741\\
		\addlinespace
		opm:verbconfirm & 0.2660910 & 0.0189728 & 54372.917 & 14.0248948 & 0.0000000\\
		opq:verbconfirm & -0.0449413 & 0.0192914 & 54373.472 & -2.3295974 & 0.0198311\\
		opc:verbdemonstrate & 0.0584268 & 0.0190633 & 54372.586 & 3.0648793 & 0.0021786\\
		opm:verbdemonstrate & 0.1781393 & 0.0189714 & 54371.707 & 9.3898743 & 0.0000000\\
		opq:verbdemonstrate & -0.0008729 & 0.0192906 & 54372.707 & -0.0452486 & 0.9639093\\
		\addlinespace
		opc:verbestablish & 0.0300718 & 0.0190618 & 54371.161 & 1.5775980 & 0.1146638\\
		opm:verbestablish & 0.1877158 & 0.0189720 & 54372.212 & 9.8943713 & 0.0000000\\
		opq:verbestablish & -0.0700678 & 0.0192899 & 54372.103 & -3.6323635 & 0.0002811\\
		opc:verbhear & -0.0253789 & 0.0190637 & 54372.970 & -1.3312665 & 0.1831069\\
		opm:verbhear & -0.1048737 & 0.0189721 & 54372.368 & -5.5277707 & 0.0000000\\
		\addlinespace
		opq:verbhear & -0.0006261 & 0.0192909 & 54372.991 & -0.0324581 & 0.9741069\\
		opc:verbinform & -0.0991359 & 0.0190633 & 54372.605 & -5.2003420 & 0.0000002\\
		opm:verbinform & -0.0860938 & 0.0189733 & 54373.368 & -4.5376355 & 0.0000057\\
		opq:verbinform & -0.0174718 & 0.0192931 & 54374.843 & -0.9055994 & 0.3651520\\
		opc:verbknow & -0.1127399 & 0.0190628 & 54372.127 & -5.9141311 & 0.0000000\\
		\addlinespace
		opm:verbknow & -0.0872392 & 0.0189719 & 54372.149 & -4.5983336 & 0.0000043\\
		opq:verbknow & -0.0192684 & 0.0192895 & 54371.814 & -0.9989027 & 0.3178463\\
		opc:verbpretend & -0.3172145 & 0.0190639 & 54373.134 & -16.6395086 & 0.0000000\\
		opm:verbpretend & -0.1196669 & 0.0189725 & 54372.658 & -6.3073967 & 0.0000000\\
		opq:verbpretend & -0.2959105 & 0.0192916 & 54373.627 & -15.3388172 & 0.0000000\\
		\addlinespace
		opc:verbprove & 0.0309486 & 0.0190626 & 54371.908 & 1.6235265 & 0.1044827\\
		opm:verbprove & 0.2578102 & 0.0189728 & 54372.987 & 13.5883819 & 0.0000000\\
		opq:verbprove & -0.0531478 & 0.0192907 & 54372.839 & -2.7550974 & 0.0058694\\
		opc:verbreveal & 0.0632551 & 0.0190641 & 54373.234 & 3.3180321 & 0.0009071\\
		opm:verbreveal & 0.0765052 & 0.0189711 & 54371.383 & 4.0327309 & 0.0000552\\
		\addlinespace
		opq:verbreveal & -0.0096396 & 0.0192917 & 54373.669 & -0.4996755 & 0.6173056\\
		opc:verbsay & -0.0284748 & 0.0190633 & 54372.590 & -1.4936938 & 0.1352615\\
		opm:verbsay & 0.0449550 & 0.0189713 & 54371.586 & 2.3696339 & 0.0178092\\
		opq:verbsay & -0.2578020 & 0.0192911 & 54373.227 & -13.3637456 & 0.0000000\\
		opc:verbsee & -0.0094907 & 0.0190633 & 54372.613 & -0.4978528 & 0.6185898\\
		\addlinespace
		opm:verbsee & -0.0408332 & 0.0189714 & 54371.728 & -2.1523480 & 0.0313743\\
		opq:verbsee & 0.0345992 & 0.0192916 & 54373.623 & 1.7934827 & 0.0729013\\
		opc:verbthink & -0.2246902 & 0.0190628 & 54372.159 & -11.7868151 & 0.0000000\\
		opm:verbthink & -0.0856847 & 0.0189719 & 54372.175 & -4.5163904 & 0.0000063\\
		opq:verbthink & -0.2500624 & 0.0192911 & 54373.178 & -12.9625865 & 0.0000000\\
		\bottomrule
	\end{tabular}
\end{table}

\begin{table}[ht]
	\caption{Model output w \texttt{know/n} as baseline}
	\label{tab:discover-n}
	\centering

	\begin{tabular}{lrrrrr}
		\toprule
		  & Estimate & Std. Error & df & t value & Pr(>|t|)\\
		\midrule
		(Intercept) & 0.7921005 & 0.0114401 & 1479.182 & 69.2391632 & 0.0000000\\
		opc & -0.0013151 & 0.0156638 & 26226.099 & -0.0839558 & 0.9330922\\
		opm & -0.1434448 & 0.0155855 & 26286.727 & -9.2037503 & 0.0000000\\
		opq & 0.0818736 & 0.0143093 & 56827.205 & 5.7217106 & 0.0000000\\
		verbdiscover & -0.1115762 & 0.0134931 & 54371.661 & -8.2691029 & 0.0000000\\
		\addlinespace
		verbbe\_annoyed & 0.0748953 & 0.0134936 & 54372.286 & 5.5504198 & 0.0000000\\
		verbsuggest & -0.5413729 & 0.0134928 & 54371.215 & -40.1230775 & 0.0000000\\
		verbacknowledge & -0.1455464 & 0.0134940 & 54372.778 & -10.7859911 & 0.0000000\\
		verbadmit & -0.2653476 & 0.0134936 & 54372.243 & -19.6647018 & 0.0000000\\
		verbannounce & -0.2858550 & 0.0134935 & 54372.051 & -21.1847253 & 0.0000000\\
		\addlinespace
		verbbe\_right & -0.5889971 & 0.0134936 & 54372.234 & -43.6501264 & 0.0000000\\
		verbconfess & -0.2932742 & 0.0134933 & 54371.896 & -21.7347532 & 0.0000000\\
		verbconfirm & -0.5589410 & 0.0134943 & 54373.134 & -41.4204989 & 0.0000000\\
		verbdemonstrate & -0.4558072 & 0.0134931 & 54371.605 & -33.7807521 & 0.0000000\\
		verbestablish & -0.4793608 & 0.0134938 & 54372.501 & -35.5245129 & 0.0000000\\
		\addlinespace
		verbhear & -0.1207841 & 0.0134931 & 54371.608 & -8.9515418 & 0.0000000\\
		verbinform & -0.0625474 & 0.0134940 & 54372.811 & -4.6351853 & 0.0000036\\
		verbpretend & -0.4300580 & 0.0134939 & 54372.685 & -31.8704317 & 0.0000000\\
		verbprove & -0.5615997 & 0.0134934 & 54372.014 & -41.6202578 & 0.0000000\\
		verbreveal & -0.2308861 & 0.0134943 & 54373.179 & -17.1098402 & 0.0000000\\
		\addlinespace
		verbsay & -0.4670771 & 0.0134939 & 54372.578 & -34.6140392 & 0.0000000\\
		verbsee & -0.1078558 & 0.0134932 & 54371.715 & -7.9933523 & 0.0000000\\
		verbthink & -0.4352245 & 0.0134933 & 54371.896 & -32.2547883 & 0.0000000\\
		opc:verbdiscover & 0.1127399 & 0.0190628 & 54372.122 & 5.9141311 & 0.0000000\\
		opm:verbdiscover & 0.0872392 & 0.0189719 & 54372.145 & 4.5983336 & 0.0000043\\
		\addlinespace
		opq:verbdiscover & 0.0192684 & 0.0192895 & 54371.810 & 0.9989027 & 0.3178463\\
		opc:verbbe\_annoyed & -0.1142699 & 0.0190629 & 54372.206 & -5.9943630 & 0.0000000\\
		opm:verbbe\_annoyed & -0.0130032 & 0.0189709 & 54371.180 & -0.6854301 & 0.4930755\\
		opq:verbbe\_annoyed & -0.0569598 & 0.0192897 & 54371.974 & -2.9528580 & 0.0031498\\
		opc:verbsuggest & 0.0451626 & 0.0190614 & 54370.865 & 2.3693169 & 0.0178244\\
		\addlinespace
		opm:verbsuggest & 0.1636081 & 0.0189713 & 54371.561 & 8.6239932 & 0.0000000\\
		opq:verbsuggest & -0.1307246 & 0.0192896 & 54371.847 & -6.7769511 & 0.0000000\\
		opc:verbacknowledge & 0.0802870 & 0.0190639 & 54373.059 & 4.2114778 & 0.0000254\\
		opm:verbacknowledge & 0.0970521 & 0.0189731 & 54373.215 & 5.1152465 & 0.0000003\\
		opq:verbacknowledge & 0.0103337 & 0.0192900 & 54372.183 & 0.5357031 & 0.5921659\\
		\addlinespace
		opc:verbadmit & 0.1660650 & 0.0190633 & 54372.568 & 8.7112405 & 0.0000000\\
		opm:verbadmit & 0.1680676 & 0.0189725 & 54372.674 & 8.8584875 & 0.0000000\\
		opq:verbadmit & -0.0129548 & 0.0192897 & 54371.901 & -0.6715939 & 0.5018451\\
		opc:verbannounce & 0.1361230 & 0.0190629 & 54372.249 & 7.1407107 & 0.0000000\\
		opm:verbannounce & 0.1502994 & 0.0189716 & 54371.859 & 7.9223393 & 0.0000000\\
		\addlinespace
		opq:verbannounce & -0.0552066 & 0.0192897 & 54371.911 & -2.8619784 & 0.0042117\\
		opc:verbbe\_right & 0.0281618 & 0.0190625 & 54371.883 & 1.4773357 & 0.1395915\\
		opm:verbbe\_right & 0.2452367 & 0.0189720 & 54372.236 & 12.9262410 & 0.0000000\\
		opq:verbbe\_right & -0.1346444 & 0.0192901 & 54372.308 & -6.9799743 & 0.0000000\\
		opc:verbconfess & 0.1968531 & 0.0190627 & 54372.016 & 10.3266157 & 0.0000000\\
		\addlinespace
		opm:verbconfess & 0.1707082 & 0.0189737 & 54373.731 & 8.9971020 & 0.0000000\\
		opq:verbconfess & -0.0175959 & 0.0192891 & 54371.441 & -0.9122160 & 0.3616590\\
		opc:verbconfirm & 0.1821133 & 0.0190626 & 54371.955 & 9.5534239 & 0.0000000\\
		opm:verbconfirm & 0.3533301 & 0.0189718 & 54372.046 & 18.6239655 & 0.0000000\\
		opq:verbconfirm & -0.0256729 & 0.0192917 & 54373.707 & -1.3307729 & 0.1832693\\
		\addlinespace
		opc:verbdemonstrate & 0.1711667 & 0.0190647 & 54373.791 & 8.9782020 & 0.0000000\\
		opm:verbdemonstrate & 0.2653784 & 0.0189716 & 54371.911 & 13.9881581 & 0.0000000\\
		opq:verbdemonstrate & 0.0183955 & 0.0192903 & 54372.499 & 0.9536136 & 0.3402835\\
		opc:verbestablish & 0.1428117 & 0.0190634 & 54372.667 & 7.4914038 & 0.0000000\\
		opm:verbestablish & 0.2749549 & 0.0189719 & 54372.156 & 14.4927310 & 0.0000000\\
		\addlinespace
		opq:verbestablish & -0.0507994 & 0.0192892 & 54371.529 & -2.6335636 & 0.0084518\\
		opc:verbhear & 0.0873610 & 0.0190622 & 54371.557 & 4.5829467 & 0.0000046\\
		opm:verbhear & -0.0176345 & 0.0189709 & 54371.193 & -0.9295579 & 0.3526042\\
		opq:verbhear & 0.0186422 & 0.0192902 & 54372.432 & 0.9664076 & 0.3338446\\
		opc:verbinform & 0.0136041 & 0.0190628 & 54372.117 & 0.7136441 & 0.4754504\\
		\addlinespace
		opm:verbinform & 0.0011454 & 0.0189738 & 54373.859 & 0.0603655 & 0.9518647\\
		opq:verbinform & 0.0017966 & 0.0192921 & 54374.044 & 0.0931259 & 0.9258039\\
		opc:verbpretend & -0.2044746 & 0.0190640 & 54373.227 & -10.7256652 & 0.0000000\\
		opm:verbpretend & -0.0324277 & 0.0189726 & 54372.773 & -1.7091875 & 0.0874219\\
		opq:verbpretend & -0.2766421 & 0.0192909 & 54373.044 & -14.3405213 & 0.0000000\\
		\addlinespace
		opc:verbprove & 0.1436885 & 0.0190622 & 54371.604 & 7.5378609 & 0.0000000\\
		opm:verbprove & 0.3450493 & 0.0189712 & 54371.500 & 18.1880552 & 0.0000000\\
		opq:verbprove & -0.0338794 & 0.0192909 & 54373.040 & -1.7562330 & 0.0790543\\
		opc:verbreveal & 0.1759951 & 0.0190637 & 54372.960 & 9.2319255 & 0.0000000\\
		opm:verbreveal & 0.1637444 & 0.0189722 & 54372.374 & 8.6307727 & 0.0000000\\
		\addlinespace
		opq:verbreveal & 0.0096288 & 0.0192902 & 54372.406 & 0.4991553 & 0.6176720\\
		opc:verbsay & 0.0842652 & 0.0190632 & 54372.497 & 4.4203002 & 0.0000099\\
		opm:verbsay & 0.1321942 & 0.0189719 & 54372.094 & 6.9679113 & 0.0000000\\
		opq:verbsay & -0.2385336 & 0.0192898 & 54371.999 & -12.3658155 & 0.0000000\\
		opc:verbsee & 0.1032492 & 0.0190630 & 54372.324 & 5.4162003 & 0.0000001\\
		\addlinespace
		opm:verbsee & 0.0464060 & 0.0189718 & 54372.089 & 2.4460454 & 0.0144464\\
		opq:verbsee & 0.0538675 & 0.0192901 & 54372.298 & 2.7924979 & 0.0052321\\
		opc:verbthink & -0.1119503 & 0.0190627 & 54372.030 & -5.8727378 & 0.0000000\\
		opm:verbthink & 0.0015545 & 0.0189713 & 54371.557 & 0.0819391 & 0.9346955\\
		opq:verbthink & -0.2307940 & 0.0192903 & 54372.447 & -11.9642778 & 0.0000000\\
		\bottomrule
	\end{tabular}
\end{table}
